---
title: "Advanced Bioinformatics 2019 assessment"
author: "1806284"
date: "09/05/2019"
output:
  html_document:
    keep_md: yes
---


"Task 1"
```{r}
sum(5:55)
```




"Task 2"
```{r}
sumfun <- function(n){
  return(sum(5:n))
}

sumfun(10)
sumfun(20)
sumfun(100)
```




"Task 3"
```{r}
vector<-c()
vector[1:2]=1
for (i in 3:12){
  vector[i]=vector[i-1]+vector[i-2]
}
 
vector 
```




"Task 4"
```{r}
data(mtcars)
library(ggplot2)

ggplot(mtcars, aes(x=factor(gear),y=mpg,fill=factor(gear)))+
  geom_boxplot(notch=F) +scale_x_discrete("Gear")+
  scale_y_continuous("Miles per Gallon")+ggtitle("MPG by Gears")
```





"Task 5"
```{r}
data(cars)
lmodel <- lm(dist ~ speed, data = cars)

slope <- lmodel$coefficients[2]
slope[[1]]
intercept <- lmodel$coefficients[1]
intercept[[1]]

sd_slope <- summary(lmodel)$coefficients[2,2]
sd_slope
sd_intercept <- summary(lmodel)$coefficients[1,2]
sd_intercept
```





"Task 6"
```{r}
ggplot(cars, aes(x=speed, y=dist)) + geom_point() + labs(y="Breaking Distance [feet]", x="Speed [mph]") +
  geom_smooth(method="lm", se=F)
  #geom_abline(intercept = 8.28, slope=0.16)

```





"Task 7"
```{r}

speed_t <- cars$speed * (5280/3600)

lmodel_2 <- lm(dist ~ 0 + speed_t + I(speed_t^2), cars)
summary(lmodel_2)

# The average value is 0.84479 seconds, which seems a reasonable time

x <- cars$spped_t
y <- cars$dist

ggplot(cars,aes(speed_t, dist)) +
  geom_point()+
  geom_smooth(method="lm", formula = "y~0+x+I(x^2)")+
  labs(title="Average reaction time", x="Speed [feets/s]", y="Breaking distance [feet]")

```


When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

